The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to paper

\begin{abstract}
	This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.  This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in prime characteristic commutative algebra.
\end{abstract}

@@

This paper describes the \emph{Macaulay2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in prime characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.  Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F : R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).  The notion of $F$-purity first appeared in the work of Hochster and Roberts in \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.

After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.

Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  
The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
Furthermore, the more general \emph{$F$-thresholds} was also introduced, a family that contains the $F$-pure threshold. 
These numerical invariants are typically very difficult to calculate, and due to their significance, have been the 
focus of intense study over the past fifteen years.
This \emph{Macaulay2} package is centered around calculating 
and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.

@@

\end{MyVerbatim}

>>>>

\begin{abstract}
   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in positive characteristic commutative algebra.
\end{abstract}

@@

This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
The notion of $F$-purity first appeared in the work of Hochster and Roberts \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.

After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.

Along these lines, the notion of the \emph{$F$-pure threshold} was defined in analogy with the \emph{log canonical threshold} \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  
The $F$-pure threshold of the pair $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure.  
Furthermore, the more general notion of \emph{$F$-thresholds}, which includes the $F$-pure threshold, was also introduced. 
These numerical invariants are typically very difficult to calculate, and due to their significance, have been the focus of intense study over the past fifteen years.
This \emph{Macaulay2} package is centered around calculating and estimating the $F$-pure threshold and other $F$-thresholds, with the function {\tt fpt} at its core.

@@
